## Evolutionary History of the Main Biological Characters of Siphonophores

### 2017-02-14 character_coding/CharacterEvolution.Rmd

When we reconstruct the evolutionary history of sex distribution in siphonophore species, we obtain the following results:
```{r sex_results} 
make.simmap(ultratree, sex, nsim = 100)
```

@@

###Number of Bract types:
```{r bract_types}
#Simmap bract-types
plotTree(ultratree, lwd = 4)
bracts_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red", "green3", "blue")
names(colors) = c("No bracts", "1", "2", "4")
nodelabels(pie=(describe.simmap(bracts_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
```

@@

##Continuous traits: Brownian motion reconstructions

```{r cont_bract_types, echo=F, message=F, warning=F}
contMap(ultratree, bracts)
```

###Median depth reconstruction:
```{r median_cont, echo=F, message=F, warning=F}
depth_value = depth_median
depthmap <- contMap(dpruned_tree, depth_value) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap)
```

###Bathymetrics phylomorphospace
```{r depth_phylomorpho, echo=F, message=F, warning=F}
par(oma=rep(4,4))
phylomorphospace(depthmap$tree, cbind(depth_max, depth_min), xlab="Minimum depth (m)", ylab="Maximum depth (m)", colors=depthmap$cols, fsize=0.8, label = "horizontal")

#with time from root...
evotime = fastBM(dpruned_tree,nsim=2)
evotime_map <- contMap(dpruned_tree,evotime[,1])
evotime_map$cols[]<-rainbow(1001,start=0.7,end=0)
phylomorphospace(evotime_map$tree, cbind(depth_max, depth_min), xlab="Minimum depth (m)", ylab="Maximum depth (m)", colors=evotime_map$cols, fsize=0.8, label = "horizontal")
#add.color.bar(2,evotime_map$cols,title="Time from the root", lims=c(0,2000),digits=5)
```

@@

###Phylogenetic signal in VARS bathymetrics
```{r phylosig_depth, echo=F, message=F, warning=F}
physignal(dpruned_data[,c(13,14,15,17,18)], dpruned_tree)
physignal(depth_range, dpruned_tree)
multiPhylosignal(dpruned_data[,c(13,14,15,17,18)], dpruned_tree)
```

>>>>

When we reconstruct the evolutionary history of different traits in siphonophore species, we obtain the following results:

@@

###Number of Bract types:
```{r bract_types, echo=F, message=F, warning=F}
#Simmap bract-types
plotTree(ultratree, lwd = 4)
bracts_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red", "green3", "blue")
names(colors) = c("No bracts", "1", "2", "4")
nodelabels(pie=(describe.simmap(bracts_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
```

@@

##Continuous traits: Brownian motion reconstructions
###Number of bract types reconstruction:
```{r cont_bract_types, echo=F, message=F, warning=F}
contMap(ultratree, bracts)
```

###Median depth reconstruction:
```{r median_cont, echo=F, message=F, warning=F}
depth_value = depth_median
depthmap <- contMap(dpruned_tree, depth_value, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap)
```

###Bathymetrics phylomorphospace
```{r depth_phylomorpho, echo=F, message=F, warning=F}
par(oma=rep(4,4))
phylomorphospace(depthmap$tree, cbind(depth_max, depth_min), xlab="Minimum depth (m)", ylab="Maximum depth (m)", colors=depthmap$cols, fsize=0.8, label = "horizontal")
```

###Bathymetrics phylomorphospace with time from root as color
```{r depth_phylochronomorpho, echo=F, message=F, warning=F}
evotime = fastBM(dpruned_tree,nsim=2)
evotime_map <- contMap(dpruned_tree,evotime[,1], plot=F)
evotime_map$cols[]<-rainbow(1001,start=0.7,end=0)
phylomorphospace(evotime_map$tree, cbind(depth_max, depth_min), xlab="Minimum depth (m)", ylab="Maximum depth (m)", colors=evotime_map$cols, fsize=0.8, label = "horizontal")
#add.color.bar(2,evotime_map$cols,title="Time from the root", lims=c(0,2000),digits=5)
```

@@

###Phylogenetic signal in VARS bathymetrics
```{r phylosig_depth, echo=F, message=F, warning=F}
physignal(dpruned_data[,c(13,14,15,17,18)], dpruned_tree)
multiPhylosignal(dpruned_data[,c(13,14,15,17,18)], dpruned_tree)
```
